The sweet spot for local polygenic adaptation: a case study motivated by stickleback

### 2018-08-21 Stickleback_Paper.tex
latest changes

\paragraph{Habitat and geography}
Our model has two habitat types, which are considered separate populations
with a fixed total size of 2,000 diploid individuals each. The marine population is treated as a single large deme, but the freshwater population is subdivided into local subpopulations or demes.
The scheme, depicted in Figure \ref{fig:Geo},
roughly models a set of freshwater habitats
along a stretch of coastline.
The ``marine'' habitat  is a continuous, one-dimensional range of 10 units of length,
and the ``freshwater'' habitat is divided into ten subpopulations
(which we call ``lakes''), each connected to the marine habitat
at positions $i - 1/2$ for $1 \le i \le 10$.

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.6\linewidth]{GeographyFigure}
  		\caption{A representation of the geographic and evolutionary history of all populations throughout the simulation. 
		The marine is a one-dimensional, continuous population with spatial positions ranging from [0.0 - 10.0]. 
		Each freshwater lake$_{i}$ for both the introduced and freshwater populations
		is a discrete population connected by migration only through the marine, at position $i - 0.5$. 
		The introduced lakes have the same spatial location (but separate?) and selective pressure as the original lakes, but arise at 40K generations.
		The marine has $2000$ diploid individuals while each of the lakes fluctuate around $200$. 
		the introduced population is initialized as a copy of all marine individuals to model marine 
		individuals inhabiting a newly created freshwater environment such as the ponds around Middleton Island.
		We then observe the selection process of marine individuals and following generations 
		with the new selective pressure across a range of parameter values. 
		%Migration between the marine and original lakes is 
		%set to $0$ the generation before introduction to avoid direct migrants from original $->$ introduced lakes.
		}
  		\label{fig:Geo}
	\end{center}
\end{figure}

>>>>

\paragraph{Habitat and geography}
Our model has two habitat types, which are considered separate populations
with a fixed total size of 5,000 diploid individuals each. The marine population is treated as a single large deme, but the freshwater population is subdivided into local subpopulations or demes.
The scheme, depicted in Figure \ref{fig:Geo},
roughly models a set of freshwater habitats
along a stretch of coastline.
The ``marine'' habitat  is a continuous, one-dimensional range of 25 units of length,
%%%%
and the ``freshwater'' habitat is divided into ten subpopulations
(which we call ``lakes''), each connected to the marine habitat
at positions $i - 1/2$ for $1 \le i \le 10$.

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.6\linewidth]{GeographyFigure.pdf}
  		\caption{A representation of the geographic and evolutionary history of all populations throughout the simulation. 
		The marine is a one-dimensional, continuous population with spatial positions ranging from [0.0 - 10.0]. 
		Each freshwater lake$_{i}$ for both the introduced and freshwater populations
		is a discrete population connected by migration only through the marine, at position $i - 0.5$. 
		The introduced lakes have the same spatial location (but separate?) and selective pressure as the original lakes, but arise at 40K generations.
		The marine has $2000$ diploid individuals while each of the lakes fluctuate around $200$. 
		the introduced population is initialized as a copy of all marine individuals to model marine 
		individuals inhabiting a newly created freshwater environment such as the ponds around Middleton Island.
		We then observe the selection process of marine individuals and following generations 
		with the new selective pressure across a range of parameter values. 
		%Migration between the marine and original lakes is 
		%set to $0$ the generation before introduction to avoid direct migrants from original $->$ introduced lakes.
		}
  		\label{fig:Geo}
	\end{center}
\end{figure}
